Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-05 ppdp24/hyper.tex
checkpoint

\begin{definition}[Malicious Correctness]
  A protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is \emph{malicious correct} iff
  $
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) \supseteq
    \support(\progtt(\prog,\adversary)(O_H|\store))
  $.
\end{definition}

@@

@@

\begin{definition}[Robust Declassification]
  A protocol satisfies \emph{robust declassification} iff it has integrity and
  satisfies gradual release. 
\end{definition}

\begin{theorem}
  Robust declassification does not imply malicious security, but
  passive security with robust declassification implies malicious security.
\end{theorem}

>>>>

%\begin{definition}[Malicious Correctness]
%  A protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is \emph{malicious correct} iff
%  $
%  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) \supseteq
%    \support(\progtt(\prog,\adversary)(O_H|\store))
%  $.
%\end{definition}

@@

\begin{lemma}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is passive correct for
  $\idealf$ and
  has integrity, then for all $H$, $C$, and $\adversary$ and $\store_1 \in \mems(S_H)$,
  there exists $\store_2 \in \mems(S_C)$ such that:
  $$
  \idealf(\store_1 \cap \store_2)_H \cup \{ \bot \} \supseteq
    \support(\progtt(\prog,\adversary)(O_H|\store_1))
  $$
\end{lemma}

@@

\begin{definition}[Robust Declassification]
  A protocol satisfies \emph{robust declassification} iff it has integrity and
  satisfies delimited release. 
\end{definition}

\begin{theorem}
  Robust declassification does not imply malicious security, but
  security with robust declassification implies malicious security.
\end{theorem}
